\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{float}
\usepackage{graphicx}
\usepackage{array}
\usepackage{microtype}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=blue]{hyperref}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,fit}

\title{L20-CodeForge: Auditable Test-Time Scaling for Code Generation on a Single GPU}
\author{Yin Li\\University of Birmingham}
\date{May 2026}

\begin{document}
\maketitle

\begin{abstract}
Large code models are often evaluated in settings that assume substantial
serving budgets, broad sampling, and opaque benchmark pipelines. This paper
studies a narrower question: how much reliable coding performance can be
extracted from a 7B-class open model when the compute budget is a single NVIDIA
L20 GPU and hidden tests are reserved for measurement. We describe
L20-CodeForge, an auditable post-training and inference stack for code
generation. The system separates public-side candidate generation, public-test
selection, repair, and verifier experiments from private hidden-test replay. On
the full 1,055-task LiveCodeBench \texttt{release\_v6} code-generation suite,
Qwen2.5-Coder-7B-Instruct improves from 297 solved tasks under greedy decoding
to 403 solved tasks with eight-sample public-test selection, a gain of 10.05
percentage points. On EvalPlus, the clean public-signal system improves
HumanEval+ from 84.8\% to 92.7\% and MBPP+ from 72.2\% to 81.7\%. We also
report negative results: repeated public-feedback repair can overfit visible
tests, input-only differential tests do little without multiple
public-passing candidates, and an uncalibrated expected-output verifier can
regress hidden replay. The main claim is not that a new model checkpoint
outperforms the base model; rather, the result is a reproducible case study in
benchmark hygiene, test-time scaling, and failure-aware post-training
infrastructure under a small-GPU constraint.
\end{abstract}

\section{Introduction}

Execution is both the advantage and the trap of code generation. It gives a
cheap verifier for many tasks, but it also creates easy ways to overstate
progress: select on visible examples, tune against stale hidden tests, or report
small optimistic subsets. This tension is sharper for resource-constrained
post-training. A single accelerator cannot support the search budgets or
training sweeps used by large labs, so every evaluation decision carries more
weight.

This paper reports a small-GPU study rather than a new frontier model. We use a
single NVIDIA L20 as the target hardware and ask what can be gained by improving
the surrounding system: candidate generation, public-test selection, repair,
candidate health auditing, hidden replay, and cross-benchmark scorecards. The
model in the main experiment is Qwen2.5-Coder-7B-Instruct. Hidden LiveCodeBench
tests are used only for final replay and audit, not for candidate selection or
repair.

The study makes four contributions.

\begin{enumerate}
    \item We define an auditable single-GPU evaluation protocol for code
    generation with a strict public/private boundary.
    \item We report full-suite LiveCodeBench \texttt{release\_v6} and EvalPlus
    results with committed artifacts, hashes, and re-run commands.
    \item We analyze several verifier and repair variants, including negative
    results that would be hidden by a headline-only report.
    \item We release the supporting repository as a reproducibility artifact
    with CI, scorecards, benchmark summaries, and exact hash checks.
\end{enumerate}

\section{Claim Boundary}

The central result in this paper is a system result. It should not be read as a
claim that the underlying Qwen2.5-Coder-7B-Instruct weights have improved. We
make three boundaries explicit.

\paragraph{System-level gains.}
The LiveCodeBench headline result uses eight sampled candidates and public-test
selection. This is a valid solver configuration, but it is different from a
single greedy model evaluation. Whenever we compare against greedy decoding, the
comparison is between a baseline model call and a bounded public-side inference
system.

\paragraph{Public signals only during selection.}
Public tests, public examples, starter code, and public prompt metadata may be
used by the solver. Hidden tests are used only after a candidate has already
been selected. No hidden expected outputs, hidden failure messages, or hidden
pass/fail labels enter generation, repair, verifier prompts, or tie-breaking.

\paragraph{Negative results remain part of the evidence.}
Several plausible improvements were rejected because they failed hidden replay
or cross-benchmark checks. These failures are reported because they define the
boundary between useful test-time scaling and visible-test overfitting.

\section{Related Work and Positioning}

\paragraph{Code-generation benchmarks.}
LiveCodeBench was introduced to reduce contamination and broaden code-model
evaluation beyond static HumanEval-style tasks, including code generation,
self-repair, code execution, and test-output prediction
\citep{jain2024livecodebench}. EvalPlus showed that common code benchmarks can
miss incorrect programs because their tests are insufficient; it augments
HumanEval and MBPP with many additional tests and can change model rankings
\citep{liu2023evalplus}. These benchmarks motivate the two evaluation choices
used here: full-suite replay on LiveCodeBench and cross-checking with EvalPlus.

Qwen2.5-Coder provides the open 7B base model used in the main experiments
\citep{qwen2024coder}. The paper does not compare against larger proprietary
systems because the research question is whether a small open model can be used
more reliably under a single-GPU budget.

\paragraph{Test-time scaling and execution-guided selection.}
AlphaCode demonstrated that large-scale sampling followed by program-behavior
filtering is central to competitive-programming performance
\citep{li2022alphacode}. CodeT generates tests and uses execution agreement to
select among samples \citep{chen2022codet}. LEVER trains an execution-aware
verifier to rerank generated programs \citep{ni2023lever}. S* studies
test-time scaling for code and reports large gains from hybrid search and
selection on LiveCodeBench \citep{li2025sstar}. L20-CodeForge follows the
same broad line of work but restricts the compute budget and emphasizes
auditable artifacts over maximum score.

\paragraph{Verified data and code RL.}
CodeRL uses unit-test and critic feedback for reinforcement learning and
test-time regeneration \citep{le2022coderl}. ACECoder synthesizes test cases to
train reward models and run code RL, reporting gains across HumanEval, MBPP,
BigCodeBench, and LiveCodeBench \citep{zeng2025acecoder}. Recent
post-training work also shows that verified competitive-programming data and
high-quality tests can substantially improve small models. rStar-Coder
constructs a large verified reasoning dataset and reports large LiveCodeBench
gains for Qwen2.5 models \citep{liu2025rstarcoder}. HardTests studies
high-quality test synthesis for difficult coding problems and finds that
stronger tests improve both evaluation and training signal
\citep{he2025hardtests}. X-Coder reports a Qwen2.5-derived RLVR model trained
with fully synthetic tasks, solutions, and tests \citep{wu2026xcoder}. These
results suggest that durable model-weight gains need verified data and
calibrated rewards, not only prompt changes.

\paragraph{Execution feedback and refinement.}
OpenCodeInterpreter integrates code generation with execution and refinement
through multi-turn feedback \citep{zheng2024opencodeinterpreter}. Reflexion
uses verbal feedback to improve language-agent behavior across tasks including
coding \citep{shinn2023reflexion}. L20-CodeForge differs in emphasis: the
repair loop is not treated as an unconstrained self-improvement process. It is
bounded by a public/private evaluation contract, and repeated feedback is
reported as a possible overfitting source when hidden replay does not improve.

\begin{table}[H]
\centering
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.25\linewidth}
                >{\raggedright\arraybackslash}p{0.30\linewidth}
                >{\raggedright\arraybackslash}p{0.34\linewidth}}
\toprule
Line of work & Main idea & Difference in this paper \\
\midrule
AlphaCode, CodeT, LEVER, S* & Sampling, execution agreement, verifier or
test-time selection & Same family of ideas, but constrained to one L20 and
reported with full artifact hashes and negative results \\
CodeRL, ACECoder & RL or reward modeling from unit tests and synthesized tests
& Treated as the next model-weight direction; the present claim remains
inference-system level \\
rStar-Coder, HardTests, X-Coder & Verified synthetic tasks, tests, and
reasoning data for stronger code models & Used as evidence that verified data
is required for durable single-sample gains \\
OpenCodeInterpreter, Reflexion & Execution/reflection feedback loops for code
or agents & This paper caps public-feedback repair and shows when repeated
feedback overfits visible tests \\
LiveCodeBench, EvalPlus & Stronger contamination and test adequacy standards
for code evaluation & Used as measurement infrastructure and as guardrails
against optimistic subset results \\
\bottomrule
\end{tabular}
\caption{Positioning against the closest research lines.}
\label{tab:positioning}
\end{table}

Taken together, this literature suggests a conservative boundary for the
present work. Public-test selection is a legitimate test-time system
intervention, but durable model-weight claims require verified training data,
calibrated reward signals, and held-out single-sample gains. The experiments
below are therefore reported as an auditable inference and post-training
infrastructure result, not as evidence that the base checkpoint has improved.

\section{Design and Protocol}

\subsection{Public and Private Signals}

Each benchmark problem is treated as two objects. The public object contains the
prompt, starter code when available, visible examples, and public tests. It may
be used for candidate generation, public-test selection, and repair. The private
object contains hidden tests. It is used only for final replay and audit.

The protocol intentionally permits public-test selection because public tests
are available to any solver. It does not permit hidden-test selection, hidden
failure feedback, or retuning against hidden outcomes. Negative outcomes are
kept in the artifact record because they identify where public-side methods fail
to generalize.

\subsection{Task Materialization}

For LiveCodeBench, the generation host receives a prompt/public-only parquet.
That file contains the problem statement, starter code where available, and
public examples/tests, but not the private tests. The full
\texttt{release\_v6} JSONL with private tests is materialized separately for
hidden replay. Its SHA-256 hash is recorded in the benchmark package; the file
itself is not committed because it is large and contains private test payloads.

Each saved generation file is immutable once it becomes a reported artifact.
Later selection and audit steps read from saved generations rather than
regenerating candidates. This makes the selection protocol inspectable and
prevents accidental score drift from sampling randomness.

\subsection{Candidate Generation}

For the main LiveCodeBench run, the model is Qwen2.5-Coder-7B-Instruct. Greedy
decoding uses one completion with temperature 0. The public-selection runs use
temperature 0.8, top-p 0.95, a 2048-token completion budget, and either four or
eight samples per task. The eight-sample run reuses the first four candidates
from the four-sample run and generates only the missing candidates.

Generation is checkpointed by task so interrupted runs can resume without
discarding completed samples. This matters on the L20 because a full
eight-sample LiveCodeBench generation pass took 28,480.919 seconds.

\subsection{Public-Test Selection}

For each task, candidates are executed against public tests only. If at least
one candidate passes all public tests, the selector chooses the shortest
public-passing program. If none pass all public tests, it chooses the shortest
candidate among those with the best public score. The shortest-solution
tie-breaker is deliberately simple: it avoids hidden labels, avoids learned
reranking that would need extra calibration, and makes the selection rule easy
to audit.

The selector also records public-pass counts, selected indices, and selected
public scores. For the eight-sample LiveCodeBench run, 618 of 1,055 selected
candidates passed all public tests. Hidden replay later showed 403 hidden
passes, leaving a large public-pass/hidden-fail gap that motivates repair and
verifier work.

\subsection{Repair and Verifier Experiments}

Repair is treated as a public-side second pass. The repair prompt may include
the original problem, public examples, the candidate code, and public-test
failure messages. It may not include private failures. We evaluated three
repair variants on the X-Coder medium control slice: starter-prefix prompting,
public-only second-pass repair, and public-feedback repair.

Verifier experiments are evaluated with the same rule: they may only consume
public-side signals before selection. Candidate-aware behavior tests and
expected-output verifier prompts were therefore built from generated or public
inputs, not private labels. A verifier variant is allowed into a headline result
only if it improves hidden replay without failing the generalization scorecard.

\subsection{Hidden Replay and Scorecards}

After public-side selection, the selected candidate is replayed against private
tests using the LiveCodeBench evaluator. Hidden replay is chunked so a
single-problem worker failure does not invalidate the full run. In the reported
eight-sample run, one worker failure occurred on question id 3637; it is counted
as a hidden failure rather than omitted.

The generalization scorecard combines full LiveCodeBench with EvalPlus
HumanEval+ and MBPP+. Any future selector, repair loop, adapter, or verifier
must improve the target benchmark without failing this scorecard.

\subsection{Hardware and Model}

The target hardware is a single NVIDIA L20 GPU. The main LiveCodeBench and
EvalPlus experiments use Qwen2.5-Coder-7B-Instruct without an adapter. The
reported LiveCodeBench system result uses temperature 0.8, top-p 0.95, eight
samples per task, public-test selection, and hidden-test replay.

\section{System Modules}

Figure~\ref{fig:system} summarizes the implementation. Candidate generation and
repair are public-side operations. Hidden replay is outside the selection loop.
The scorecard combines LiveCodeBench and EvalPlus to catch benchmark-specific
overfitting.

\begin{figure}[H]
\centering
\begin{tikzpicture}[
    node distance=7mm and 10mm,
    box/.style={draw, rounded corners, align=center, minimum height=9mm, minimum width=24mm, font=\small},
    public/.style={box, fill=blue!6, draw=blue!55!black},
    verify/.style={box, fill=green!7, draw=green!45!black},
    audit/.style={box, fill=orange!10, draw=orange!70!black},
    train/.style={box, fill=violet!7, draw=violet!60!black},
    arrow/.style={-Latex, thick}
]
\node[public] (task) {Benchmark\\task};
\node[public, right=of task] (context) {Context\\builder};
\node[public, right=of context] (gen) {Candidate\\generation};
\node[verify, right=of gen] (publictest) {Public tests\\and health};
\node[verify, below=of publictest] (repair) {Repair\\feedback};
\node[verify, left=of repair] (selector) {Selector or\\verifier};
\node[audit, below=of selector] (hidden) {Hidden-test\\replay};
\node[audit, right=of hidden] (score) {Scorecard\\and hashes};
\node[audit, right=of score] (audit) {Failure\\audit};
\node[train, below=of hidden] (store) {Trajectory\\store};
\node[train, right=of store] (data) {SFT, DPO,\\RLVR data};
\node[train, right=of data] (adapter) {Small adapter\\or verifier};

\draw[arrow] (task) -- (context);
\draw[arrow] (context) -- (gen);
\draw[arrow] (gen) -- (publictest);
\draw[arrow] (publictest) -- (repair);
\draw[arrow] (repair) -- (selector);
\draw[arrow] (selector) -- (hidden);
\draw[arrow] (hidden) -- (score);
\draw[arrow] (score) -- (audit);
\draw[arrow] (audit) -- (adapter);
\draw[arrow] (adapter) -- (data);
\draw[arrow] (data) -- (store);
\draw[arrow, dashed] (store) -- (context);
\end{tikzpicture}
\caption{L20-CodeForge evaluation loop. Public signals drive generation,
selection, and repair. Private tests are reserved for final replay and audits.}
\label{fig:system}
\end{figure}

The system is organized so each stage can be rerun without changing the
contract of the adjacent stages. The context builder emits public-only prompt
records. The generator emits immutable candidate files. The selector consumes
candidate files and public execution outcomes, but never private labels. Hidden
replay consumes exactly one selected candidate per task. The scorecard then
joins benchmark summaries, hashes, and failure counts into a read-only report.
This separation is a practical guardrail: a new repair policy, verifier, or
adapter can be swapped into the public side while preserving the same hidden
replay and scorecard path.

\section{Experiments}

\subsection{LiveCodeBench}

Table~\ref{tab:lcb-main} reports the main full-suite LiveCodeBench result. The
greedy baseline solves 297 of 1,055 tasks. Four-sample public-test selection
solves 378 tasks. Eight-sample selection solves 403 tasks, an absolute gain of
106 tasks over greedy decoding.

\begin{table}[H]
\centering
\begin{tabular}{llrrrr}
\toprule
Model & Protocol & Samples & Solved & Total & Pass@1 \\
\midrule
Qwen2.5-Coder-7B-Instruct & greedy & 1 & 297 & 1055 & 28.15 \\
Qwen2.5-Coder-7B-Instruct & public selection & 4 & 378 & 1055 & 35.83 \\
Qwen2.5-Coder-7B-Instruct & public selection & 8 & 403 & 1055 & 38.20 \\
\bottomrule
\end{tabular}
\caption{LiveCodeBench \texttt{release\_v6} full-suite results. Public
selection uses only visible public tests; hidden tests are used for final replay.}
\label{tab:lcb-main}
\end{table}

The relative improvement from greedy decoding to eight-sample public selection
is 35.69\%. The result should be interpreted as bounded test-time scaling under
a public-test solver, not as a new model checkpoint.

The gain is not uniform across difficulty levels. Easy tasks improve from 206
to 260 solved tasks, medium tasks from 82 to 124, and hard tasks from 9 to 19.
The hard-task result remains weak in absolute terms, which is consistent with
the need for stronger algorithmic candidates rather than only better selection.

\begin{table}[H]
\centering
\begin{tabular}{lrrrrr}
\toprule
Slice & Greedy solved & System solved & Total & Greedy & System \\
\midrule
Easy & 206 & 260 & 322 & 63.98 & 80.75 \\
Medium & 82 & 124 & 383 & 21.41 & 32.38 \\
Hard & 9 & 19 & 350 & 2.57 & 5.43 \\
\bottomrule
\end{tabular}
\caption{LiveCodeBench difficulty breakdown. Values in the last two columns are
percentages.}
\label{tab:lcb-breakdown}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{lrrr}
\toprule
Platform & Solved & Total & Pass@1 \\
\midrule
AtCoder & 199 & 602 & 33.06 \\
Codeforces & 5 & 9 & 55.56 \\
LeetCode & 199 & 444 & 44.82 \\
\bottomrule
\end{tabular}
\caption{LiveCodeBench platform breakdown for the eight-sample public-selection
run. Values in the last column are percentages.}
\label{tab:lcb-platform}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{lr}
\toprule
Failure class & Count \\
\midrule
Wrong answer & 438 \\
Time limit exceeded & 147 \\
Runtime error & 66 \\
Fatal chunk failure counted as failure & 1 \\
\bottomrule
\end{tabular}
\caption{Failure classes after eight-sample public selection and hidden replay.
Wrong answers dominate, which points to algorithmic candidate quality rather
than only formatting or entrypoint repair.}
\label{tab:failures}
\end{table}

\subsection{EvalPlus}

Table~\ref{tab:evalplus} reports the EvalPlus guardrail. The clean system rows
use public prompt and base-test signals, but not EvalPlus extra tests, for
selection. Both HumanEval+ and MBPP+ improve over greedy decoding.

\begin{table}[H]
\centering
\begin{tabular}{lrrrr}
\toprule
Dataset & Greedy base & System base & Greedy plus & System plus \\
\midrule
HumanEval & 89.0 & 98.2 & 84.8 & 92.7 \\
MBPP & 82.8 & 96.0 & 72.2 & 81.7 \\
\bottomrule
\end{tabular}
\caption{EvalPlus results. Values are pass@1 percentages. The plus columns use
the stricter EvalPlus tests for scoring, not for candidate selection.}
\label{tab:evalplus}
\end{table}

\subsection{Artifacts, Hashes, and Runtime}

Table~\ref{tab:artifacts} records the main reproducibility artifacts. Long
hashes are included because they are the practical link between the paper claim
and the repository state.

\begin{table}[H]
\centering
\scriptsize
\begin{tabular}{>{\raggedright\arraybackslash}p{0.28\linewidth}
                >{\raggedright\arraybackslash}p{0.64\linewidth}}
\toprule
Artifact & SHA-256 \\
\midrule
Full LiveCodeBench JSONL & \texttt{4519422b52d7dd243358ee721ecfe94e26ab364a7af2938c8e5d170a17bcadcd} \\
Eight-sample generations & \texttt{0950cbbbfcbed6d716b2c9b556e7e9aa3626211381a95e4c6e4a367bdd95df57} \\
Eight-sample summary & \texttt{2a0ff919aa15eb9ecdf74824f7bf790a23f6d0197ef74970b6190c60e0e00772} \\
Generalization scorecard & \texttt{1eb0402378ea25732225b29d7ba367b6111ab3351e54cc7c01fa7646a7a12712} \\
EvalPlus summary & \texttt{08732bbb76450f92ef3c02fa97a163aba01f71028365072c205c5a3af45d5550} \\
\bottomrule
\end{tabular}
\caption{Artifact hashes for the reported results.}
\label{tab:artifacts}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{lr}
\toprule
Operation & Wall time / setting \\
\midrule
Eight-sample generation & 28,480.919 seconds \\
Chunked hidden replay & 449.914 seconds \\
Chunk wall-time limit & 60 seconds \\
GPU budget & single NVIDIA L20 \\
\bottomrule
\end{tabular}
\caption{Runtime and hardware summary for the main LiveCodeBench result.}
\label{tab:runtime}
\end{table}

\subsection{X-Coder Control Slice}

We also probed IIGroup/X-Coder-RL-Qwen2.5-7B on a medium-difficulty control
slice. Automatic and strict starter-prefix checks both scored 0/12. Public-only
second-pass repair reached 2/12. A single public-feedback repair round reached
4/12. A second public-feedback round produced visible-test signal but no hidden
passes. We therefore treat the first feedback round as useful but not sufficient
for broad claims.

\begin{table}[H]
\centering
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.30\linewidth}rr
                >{\raggedright\arraybackslash}p{0.30\linewidth}}
\toprule
Control experiment & Public oracle & Hidden passes & Interpretation \\
\midrule
Automatic starter prefix & 0/12 & 0/12 & No transfer from targeted first-12 probes \\
Strict starter prefix & 0/12 & 0/12 & Output control did not solve algorithms \\
Public-only repair & 2/12 & 2/12 & First non-targeted positive signal \\
Fail10 multi-source repair & 0/10 & 0/10 & More code-only samples did not help \\
Public-feedback repair & 2/10 & 2/10 & Feedback changed behavior on two tasks \\
Second feedback round & 1/8 & 0/8 & Visible-test overfit signal \\
\bottomrule
\end{tabular}
\caption{X-Coder medium control-slice repair and feedback ablations. The
combined control-slice status after public-only repair plus one feedback round
is 4/12.}
\label{tab:xcoder-ablation}
\end{table}

\section{Failure Analysis}

The main failure class on the eight-sample LiveCodeBench run is wrong answer,
not syntax or missing entrypoints. This suggests that future work should
prioritize better algorithmic candidates and stronger verifier calibration over
format-only prompting.

Several attempted improvements did not hold up under hidden replay. Repeated
public-feedback repair overfit visible tests on the second round. Input-only
differential fuzzing improved candidate-pair coverage on some targets but did
not change selection when the pool contained too few public-passing alternatives. An
expected-output verifier over generated inputs regressed the targeted replay,
indicating that verifier confidence needs calibration before it can safely alter
headline selections.

The same pattern appears in the X-Coder control slice. Public-feedback repair
is useful for one round, but a second round created a public-passing candidate
without a corresponding hidden pass. This is the failure mode the protocol is
designed to expose: visible tests can steer the model toward local fixes that
do not capture the underlying algorithm.

\section{Reproducibility}

The repository includes committed benchmark summaries, saved generations,
reports, hash manifests, and CI checks. The full hidden-test LiveCodeBench JSONL
is not committed. Instead, the repository records materialization commands,
source hashes, generation hashes, evaluator outputs, and compact summaries.

For the main LiveCodeBench result, the committed summary hash is:

\begin{center}
\small
\texttt{2a0ff919aa15eb9ecdf74824f7bf790a23f6d0197ef74970b6190c60e0e00772}
\end{center}

The generalization scorecard hash is:

\begin{center}
\small
\texttt{1eb0402378ea25732225b29d7ba367b6111ab3351e54cc7c01fa7646a7a12712}
\end{center}

The repository also includes a separate reproducibility document with expected
command outputs and artifact-hash checks.

The arXiv source package is intentionally small: \texttt{main.tex} and
\texttt{references.bib} are sufficient to rebuild the paper. Generated PDFs,
logs, and auxiliary files are excluded from version control and from the source
archive.

\section{Limitations}

The strongest limitation is that the main gain is a system-level gain, not a
model-weight gain. The eight-sample selector is useful in practice but should
not be confused with a greedy checkpoint improvement. The experiments also use
one main base model and one main GPU type. Public tests are legitimate solver
signals, but repeated repair on public failures can overfit them. Finally,
private benchmark tests cannot be committed directly, so full hidden replay
requires local materialization of the benchmark payload.

The paper is also limited by scope. It does not yet include a trained adapter
that improves greedy LiveCodeBench performance, a calibrated learned verifier,
or a verified synthetic-data pipeline comparable to rStar-Coder or X-Coder. The
appropriate next claim would require held-out single-sample gains, not only
stronger public-side selection.

\section{Conclusion}

L20-CodeForge shows that a careful single-GPU system can extract a meaningful
amount of additional coding performance from a 7B open model while preserving a
clean benchmark boundary. The useful parts are not only the positive results,
but also the audit trail: public selection helps, first-round repair can help,
and several plausible verifier variants fail without calibration. The next step
is to convert this infrastructure into a verified-data and RLVR pipeline that
improves single-sample model behavior on held-out tasks.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
